Poisson approximate likelihood compared to the particle filter

### 2024-09-03 ms.Rnw
modify with sbh init - add NA

sir_full <- pomp(
  sir_wwr,
  rinit = rinit_full,
  params = params_full,
  partrans = pt_full,
  statenames = statenames,
  paramnames = names(params_full)
)

sir_sbh_init <- pomp(
  sir_wwr,
  t0 = 1-6*52,
  rinit = rinit_stocks,
  statenames = statenames
) 
@

@@

<<maximization1-Stocks_rinit, echo=F, warning=F, message=F>>=
set.seed(123)
sir_box_sbh <- list(
  beta1 = c(10, 15),
  beta2 = c(0.2, 0.4),
  beta3 = c(0.3, 0.5),
  phi = c(0.01, 0.3),
  beta11 = c(0.1, 0.2),
  sigma_q = c(0.001, 0.1),
  sigma_xi = c(65, 70),
  gamma = c(1, 1),
  delta1 = c(1/(5*52), 1/(5*52)),
  delta2 = c(1/(55*52), 1/(55*52)),
  alpha = c(1/(78.86912*52), 1/(78.86912*52)),
  mu = c(0, 0),
  N = c(82372825, 82372825),
  omega = c(1/(1*52), 1/(1*52))
)

@@

bake(file = paste0(out_dir, "mif2_maximization/SBH_init/round_01/sbh_el_01.rds"),{
  eval_logLik_pomp(mifs_global_sbh_01, ncores, NP_MIF, 4248930)
}) -> sbh_el_01

>>>>

sir_full <- pomp(
  sir_wwr,
  rinit = rinit_full,
  params = params_full,
  partrans = pt_full,
  statenames = statenames,
  paramnames = names(params_full)
)
@

@@

<<maximization1-Stocks_rinit, echo=F, warning=F, message=F>>=
set.seed(123)

dat %>%
  rbind(data.frame(time=0,cases1=NA,cases2=NA,cases3=NA)) %>%
  arrange(time) -> dat_sbh

sir_sbh_init <- pomp(
  sir_wwr,
  data = dat_sbh,
  times = "time",
  t0 = 1-6*52,
  rinit = rinit_stocks,
  statenames = statenames
)

sir_box_sbh <- list(
  beta1 = c(10, 15),
  beta2 = c(0.2, 0.4),
  beta3 = c(0.3, 0.5),
  phi = c(0.01, 0.3),
  beta11 = c(0.1, 0.2),
  sigma_q = c(0.001, 0.1),
  sigma_xi = c(65, 70),
  gamma = c(1, 1),
  delta1 = c(1/(5*52), 1/(5*52)),
  delta2 = c(1/(55*52), 1/(55*52)),
  alpha = c(1/(78.86912*52), 1/(78.86912*52)),
  mu = c(0, 0),
  N = c(82372825, 82372825),
  omega = c(1/(1*52), 1/(1*52))
)

@@

bake(file = paste0(out_dir, "mif2_maximization/SBH_init/round_01/sbh_el_01.rds"),{
  eval_logLik_pomp(mifs_global_sbh_01, ncores, NP_MIF, 4248930)
}) -> sbh_el_01
@
